---
title: "TBA2101 AY2021 Final Exam"
author: "TBA2102: REPLACE WITH YOUR NAME"
date: "29 April 2021, 1:00 - 3:00 PM"
output: html_document
---

## Submission Instructions (for Final Exam)
- **Rename your R Markdown file `FE_[MatricNumber].rmd`**, and the output will automatically be `FE_[MatricNumber].html`. 
- Select `output: html_document`.
- Include all code chunks, so include `echo=TRUE` in all chunks.
- Replace the placeholder text, "Type your answer here.", with your own.
- Preinstall and include any `library('package_name')` statements before the exam starts. Remember that there is no Internet connection when the exam is in progress.

- You could code and type your answer in this Rmarkdown file during exam but **keep in mind that you need to copy and paste all your answer (r-chunk and text) into Essay Answer section for each question in Examplify.**
- Submit both your R Markdown file (.rmd) and HTML (.html) to the folder "Final Exam Submission" in Luminus after Examplify submission and Internet reconnection.
- This Rmarkdown file serves as a reference. **Only answers submitted in Examplify will be graded.** Zero point will be given for blank submission in Examplify even if you have submitted a complete Rmarkdown and HTML files.

## Preparation

```{r load-libraries, echo=TRUE, warning = FALSE, message = FALSE}

# general use
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(wooldridge)

# descriptive analytics
library(psych)
library(rcompanion)
library (rpivotTable)
library(EnvStats)
library(car)

# predictive/prescriptive analytics
library(TTR)
library(forecast) 
library(olsrr)
library(factoextra)
library(caret)
library(tseries) 
library(lpSolve)
```


## Question 1: CEO Salary-1 (total 10 marks)

Data set: "ceosal1" in wooldridge. This is a data set from a 1991 issue of Business Week of CEO’s salaries in 1990.  

```{r ceo-loaddta1}

# load the data set, make sure you already load `wooldridge` package

data(ceosal1)


```

The data.frame has 209 observations on 12 variables: 

- `salary`: 1990 salary, thousands $ 
- `pcsalary`: percent change salary, 1989-1990 
- `sales`: 1990 firm sales, millions $ 
- `roe`: return on equity, 1988-1990 avg 
- `pcroe`: percent change roe, 1988-1990
- `ros`: return on firm’s stock, 1988-1990
- `indus`: =1 if industrial firm 
- `finance`: =1 if financial firm
- `consprod`: =1 if consumer product firm 
- `utility`: =1 if transport or utilities 
- `lsalary`: natural log of salary 
- `lsales`: natural log of sales

In the dataset, each observation represent a CEO's salary with its respective firm characteristics.


#### (a) In the past, the proportion of CEO with salary greater than or equal to $1 million has averaged around 0.50 (i.e. population proportion for `salary` >= 1million is 0.50). Based on the sample in this dataset, is there sufficient evidence (at 5% level of significance) to conclude that the population proportion for salary being greater than or equal to $1million is equal to 0.5? State your hypotheses, conduct the hypotheses test and provide conclusions. (4 marks)



TYPE YOUR ANSWER HERE





#### (b) You are tasked to explore if CEO salaries vary across firm types.
(i) First, create a variable `firm` and label it as “1” if it is an industrial firm, “2” if it is a financial firm, “3” if it is a consumer product firm, and “4” if it is a transport or utilities firm. (1 mark)
(ii) Now, conduct the appropriate test(s) to assess if the mean CEO salary is significantly different across firm type. Present your hypotheses, the results and conclusions. (5 marks)



TYPE YOUR ANSWER HERE


## Question 2: CEO Salary-2 (total 10 marks)

Data set: "ceosal1" in wooldridge. This is a data set from a 1991 issue of Business Week of CEO’s salaries in 1990.  

```{r ceo-loaddta2}

# load the data set, make sure you already load `wooldridge` package

data(ceosal1)


```

The data.frame has 209 observations on 12 variables: 

- `salary`: 1990 salary, thousands $ 
- `pcsalary`: percent change salary, 1989-1990 
- `sales`: 1990 firm sales, millions $ 
- `roe`: return on equity, 1988-1990 avg 
- `pcroe`: percent change roe, 1988-1990
- `ros`: return on firm’s stock, 1988-1990
- `indus`: =1 if industrial firm 
- `finance`: =1 if financial firm
- `consprod`: =1 if consumer product firm 
- `utility`: =1 if transport or utilities 
- `lsalary`: natural log of salary 
- `lsales`: natural log of sales
 
Each observation represents a CEO's salary with its respective firm characteristics.
 
#### (a) Start by plotting two bivariate scatterplots.
First, plot the scatterplot of `sales` against `lsalary`. Include a plot of the best fit line using red colour and a title for the plot. Next, plot the scatterplot of `lsales` against `lsalary`, also including a plot of the best fit line in purple and . Which one of the scatterplots shows a more linear relationship? (2 marks)


TYPE YOUR ANSWER HERE


#### We would like to examine how company performance (such as `roe` and `ros`) relates to CEO salaries. 
- (i) Run a linear regression model of lsalary ~ roe + ros. Write out the fitted line. What percentage of the variance for lsalary is being explained by `roe` and `ros`? (3 marks)
- (ii) We were told that firm sales should also affect CEO's salaries. To include firm sales as an explanatory variable for `lsalary`, explain which variable (`sales` or `lsales`) would you include in the linear regression model.  Is this model statistically (with the firm sales variable you have chosen) better at predicting `lsalary` than the model (in b(i)) without the firm sales variable? (5 marks)


TYPE YOUR ANSWER HERE


## Question 3: Investment Allocation (total 10 marks)

#### Michael received $12,000 as his year-end bonus and would like to invest it. There are three types of funds that he would like to invest in. The government bond fund has a 2.75% return, the bank's fixed deposit (FDs) has a 1.5% return, and the equity fund which has a projected return of 12%. Given his risk profile, he should not allocate more than 30% (in $ value) in the equity fund and he should invest at least three times as much in the government bonds as the FDs. Assuming the year-end yields are as projected, provide Michael with advice on how he should invest his money.

 

#### (a) Write down your decision variables, the objective function, and ALL constraints that apply for this optimization problem in a table. (3 marks)

Solve this optimization problem in R. What is the optimal dollar investment for the different investment funds? Assuming the year-end yields are as expected, how much can Michael expect to gain from his investment after one year? (3 marks)

```{r ddd echo=TRUE}
 

TYPE YOUR ANSWER HERE 

```

ANSWER 

#### (b) Michael was given an additional $2000 for his Long Service award and he would like to also invest this money. Given this, how much should he invest in for each of the 3 funds? (2 marks)

 

TYPE YOUR ANSWER HERE



 

#### (c) Michael would like additional advice on how much would the returns on the fixed deposit fund have to be, minimally, to make it worth investing in. (2 marks)


 

TYPE YOUR ANSWER HERE

